SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-06-28 scipy-1.0/paper.tex
First round of revisions for manuscript PR 34 based on reviewer comments for the draft roadmap.

In general, we encourage changes that improvie clarity in the API of the library,
but strongly discourage breaking backwards compatibility, given our position near
the base of the scientific Python computing stack.

@@

\texttt{scipy.integrate} now has a new ODE solver interface, and we should aim
to gracefully deprecate the older API. Support for integrating complex-valued
functions and integrating multiple intervals could be beneficial.

@@

\texttt{scipy.sparse} is fairly mature now, but there are many data
formats and the community continues to move forward here so we will aim
to take advantage of their improvements while preserving backwards
compatibility to the extent that it is possible. \texttt{sparse.linalg}
may benefit from wrappers for PROPACK for faster sparse SVD computation.

>>>>

In general, we encourage changes that improve clarity in the API of the library,
but strongly discourage breaking backwards compatibility, given our position near
the base of the scientific Python computing stack.

@@

\texttt{scipy.integrate} has a new ODE solver interface, and we should aim
to gracefully deprecate the older API. Support for integrating complex-valued
functions and integrating multiple intervals could be beneficial.

@@

While \texttt{scipy.sparse} is mature, there are many data
formats and the community continues to move forward here so we will aim
to take advantage of their improvements while preserving backwards
compatibility to the extent that it is possible. \texttt{sparse.linalg}
may benefit from wrappers for PROPACK for faster sparse SVD computation.
